Revisiting the impact of deepfake technology towards viewer's political choice: A replication of Soubhik Barari (2021)

### 2021-03-19 outputs/paper/paper.Rmd
update

The slip plot (Figure \@ref(fig:fs)) shows the feature selection results.  As we can see, `PID` partisanship is the most vital variable to affect the sentiment score towards Warren. As we know, partisanship is one of the most important factors affecting voters' voting. In us, there is a large group of fanatic political supporters. They don’t care about who is the candidate, or what those candidates’ ideas are. They just vote for the right party. Warren is a representative of the Democratic Party, so voters who are optimistic about the Democratic Party are willing to give higher sentiment scores. On the other hand, people who are in the Republican party and the Independent party would not support Warren.

```{r fs, fig.cap = "feature importance", echo=FALSE, warning=FALSE,fig.width=6, fig.height=6 }
# more codes are in the scripts (path: scripts/02_feature selection)
FS<- dat%>%
  select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake,exp_2,exp_2_prompt_accuracy,exp_2_after_debrief,exp_2_prompt,Zip,believed_true))%>% na.omit()

# include the plot from script
library(here)
knitr::include_graphics(here::here("outputs/paper/Variable importance plot.png"))

## remove low importance feature 
FS<- FS%>%select(-c(script_loans,quality,Hispanic))

@@

```{r diagnostic, fig.cap = "Regression diagnostics", echo=FALSE, warning=FALSE, fig.width=8, fig.height=8}
par(mfrow = c(2, 2))
plot(model)
```

@@

## Appendix A {#appendixA}
Missing value in the 
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}

>>>>

The slip plot (Figure \@ref(fig:fs1)) shows the feature selection results.  As we can see, `PID` partisanship is the most vital variable to affect the sentiment score towards Warren. As we know, partisanship is one of the most important factors affecting voters' voting. In us, there is a large group of fanatic political supporters. They don’t care about who is the candidate, or what those candidates’ ideas are. They just vote for the right party. Warren is a representative of the Democratic Party, so voters who are optimistic about the Democratic Party are willing to give higher sentiment scores. On the other hand, people who are in the Republican party and the Independent party would not support Warren. 
```{r fs1, fig.cap = "feature importance", echo=FALSE, warning=FALSE,fig.width=6, fig.height=6 }
# more codes are in the scripts (path: scripts/02_feature selection)
FS<- dat%>%
  select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake,exp_2,exp_2_prompt_accuracy,exp_2_after_debrief,exp_2_prompt,Zip,believed_true))%>% na.omit()

# build feature selection model

set.seed(123)

FS_tree<-randomForest(post_favor_Warren~., data=FS, ntree=500, importance=TRUE,proximity=TRUE) ## variable importance

FS_tree<-as.data.frame(FS_tree$importanceSD) # transform to dataframe

FS_tree<- FS_tree[order(-FS_tree[,]),,drop=FALSE] # sort importance by descending order

FS_tree<- cbind(Variable_name = rownames(FS_tree), FS_tree)

rownames(FS_tree) <- 1:nrow(FS_tree)

FS_tree<- as.data.frame(FS_tree)

# create a slip plot for feature importance 
FS_tree%>%
  mutate(name = fct_reorder(FS_tree$Variable_name,FS_tree$`FS_tree$importanceSD`))%>%
  ggplot(aes(x=FS_tree$Variable_name, y=FS_tree$`FS_tree$importanceSD`)) +
  geom_segment( aes(x=FS_tree$Variable_name,xend=FS_tree$Variable_name, y=0, yend=FS_tree$`FS_tree$importanceSD`), color="grey") +
  geom_point( color="orange", size=4) +
  theme_light() +
  coord_flip()+
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  xlab("") +
  ylab("Importance value")+
  ggtitle("Variable importance plot")
## remove low importance feature 
FS<- FS%>%select(-c(script_loans,quality,Hispanic))

@@

```{r diagnostic, fig.cap = "Regression diagnostics", echo=FALSE, warning=FALSE, fig.width=6, fig.height=6}
par(mfrow = c(2, 2))
plot(model)
```

@@

## Appendix A {#appendixA}
Missing value in the dataset. 
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}
